WASP-4\lowercase{b} Arrived Early for the TESS Mission

### 2018-12-16 paper/ms.tex
update paper

\documentclass[12pt,twocolumn,tighten]{aastex62}
%\pdfoutput=1 %for arXiv submission
\usepackage{amsmath,amstext,amssymb}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}
\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{comment}
\usepackage{todonotes}

@@

\begin{abstract}
    The Transiting Exoplanet Survey Satellite (TESS) recently observed
    18 transits of the hot Jupiter WASP-4b.  The sequence of transits
    occurred $81.5 \pm 11.8$~seconds earlier than had been predicted,
    based on earlier data stretching back to 2007.  This is unlikely
    to be the result of a clock error, because TESS observations of
    other hot Jupiters (WASP-6b, 18b, and 46b) are compatible with a
    constant period, ruling out an 81.5-second offset at the
    6.3$\sigma$ level.  The 1.3-day orbital period of WASP-4b appears
    to be decreasing at a rate of $\dot{P} = -12.6 \pm 1.2$
    milliseconds per year.  This might be caused by tidal orbital
    decay or apsidal precession, although both interpretations have
    shortcomings.  The gravitational influence of a third body is another
    possibility, although at present there is scant evidence for such a
    body. Further observations are needed to confirm and
    understand the timing variation.
\end{abstract}

@@

\section{Introduction}
\label{sec:intro}

@@

\section{New transits and system parameters}
\label{sec:observations}

\begin{figure}[t!]
    \begin{center}
        \includegraphics[width=0.49\textwidth]{f2.png}
    \end{center}
    \vspace{-0.5cm}
    \caption{
      {\bf TESS observations of WASP-4b.} On the left, black points
      are TESS flux measurements, with a vertical offset applied. Blue
      curves are best-fit models. The numbers printed next to each
      lightcurve are the approximate transit times expressed in
      BJD minus 2{,}457{,}000.  The right side shows the
      residuals.
       \label{fig:lightcurves}
    }
\end{figure}

\begin{figure}[t!]
    \begin{center}
        \includegraphics[width=0.49\textwidth]{f1.png}
    \end{center}
    \vspace{-0.5cm}
    \caption{
        {\bf Phase-folded lightcurve of WASP-4b.} Black points are
        TESS data. Yellow points are binned measurements.  The bottom
        panel shows the residuals.  The fit to the phase-folded
        transit (blue line) is used when measuring mid-transit times for
        the individual transits (Figure~\ref{fig:lightcurves}).
        \label{fig:phasefold}
    }
\end{figure}

@@

\begin{figure}[t!]
    \begin{center}
        \leavevmode
        \includegraphics[width=0.49\textwidth]{f3.pdf}
    \end{center}
    \vspace{-0.6cm}
    \caption{ {\bf TESS saw WASP-4b transit earlier than expected.}
      Both plots show the deviations between the observed and
      calculated transit times, where the calculation is based only on
      the pre-TESS data and assumes a constant period.  The blue bands
      depict the $\pm$$1\sigma$ credible interval of the predicted
      times.  {\it Top:} The full timing dataset spans 10 years. The
      darkest points correspond to the most precise data.  {\it
        Bottom:} Close-up of the TESS observations. The red band shows
      the average deviation of the TESS data, which is $81.5 \pm
      11.8\ {\rm seconds}$.
        \label{fig:arrived_early}
    }
\end{figure}

Using the cleaned PDC lightcurve, we used the Box Least Squares
algorithm \citep{kovacs_box-fitting_2002} to estimate the orbital
period, transit duration, and a reference epoch using the TESS data
alone.  Based on the results, we isolated the data within 4 transit
durations of each transit midpoint.  We then fitted all of the transit
data using the analytic formulae given by \citet{mandel_analytic_2002}
and implemented by \citet{kreidberg_batman_2015}.  We assumed the
orbit to be circular. The free parameters were the reference epoch,
the planet to star radius ratio $R_{\rm p}/R_\star$, the orbital
distance to stellar radius ratio $a/R_\star$, the inclination $i$, two
quadratic limb-darkening coefficients $(u_{\rm linear}, u_{\rm
  quad})$, and the orbital period $P$.
% JNW: Luke, didn't you also have to fit a linear trend for each transit?
% Otherwise the fit would be poor, for each transit, even if the
% trends tend to cancel out in the phase folded light curve.
% And, did you assign the photometric uncertainties as described below?

@@

To verify that the measured uncertainties are plausible, we computed
the reduced $\chi^2$ for a linear ephemeris fit to the measured TESS
transit times.  We found that $\chi^2 = 9.2$, with $n=16$ degrees of
freedom.  The variance of the $\chi^2$ distribution is $2n$, so we
would expect $\chi^2 16 \pm 5.7$.  Visually inspecting the residuals
showed that the error variance had been overestimated, so we
multiplied the measured TESS errors by a factor $f=0.76$, forcing a
reduced $\chi^2$ of unity.  This lowered the mean uncertainty of the
transit midtimes from $29.8$ to $22.6$ seconds.

Figure~\ref{fig:lightcurves} shows the lightcurve of each transit, the
best-fit models, and the residuals.  Table~2 reports the mid-transit
times and their uncertainties.  After binning the residuals to 1-hour
windows, the lightcurves have an rms scatter of 586\,{\rm ppm}.  The
pre-launch TESS noise model \citep{winn_photonflux_2013,Sullivan_2015}
\footnote{\url{github.com/lgbouma/tnm}} would have predicted an error
budget consisting of the following terms added in quadrature:
410\,{\rm ppm} from photon-counting noise, 202\,{\rm ppm} from
detector read noise, and 673\,{\rm ppm} from the zodiacal background
light.  The level of background light appears to have been
overestimated.

@@

\section{Timing analysis}
\label{sec:timing}

\begin{figure*}[t!]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{ {\bf Timing residuals and best-fit models for WASP-4b.}
		The residuals are the observed times minus the calculated times
		assuming a constant period.  The darkest points correspond to
		the most precise data. The constant-period model (gray line) is
		a poor description of the data.  Models with a uniformly
		decreasing period (blue) or apsidal precession (orange) provide
		better fits to the data.  The red square represents the
		combination of all the TESS data and is for display purposes
		only.  The models were fitted to all of the individual transit
		times.
		\label{fig:times}
	}
\end{figure*}

@@

\section{Interpretation}
\label{sec:implications}

\begin{figure}[!t]
  \begin{center}
    \includegraphics[width=0.40\textwidth]{f5.pdf}
  \end{center}
  \vspace{-0.5cm}
  \caption{
    {\bf WASP-4b in the context of other hot Jupiters.}
    Most of the data in these plots are from \citet{bonomo_gaps_2017},
    who measured the eccentricities using radial velocities.  The
    colored symbols highlight WASP-4, WASP-12 (which also shows
    evidence for a decreasing period), and the collection of hot
    Jupiters analyzed in Appendix A.
    {\bf \it Top:}
    The key parameters relevant to eccentricity damping.  Solid
    squares represent planets with a securely detected nonzero
    eccentricity. Lines of constant damping timescale are drawn based
    on Equation~\ref{eq:de_dt} and assuming $Q_{\rm p}' = 10^5$.
    WASP-4b has one of the shortest eccentricity damping timescales.
    {\bf \it Middle:} 
    Plotted are the key parameters relevant to orbital decay.  Lines
    of constant decay timescale are drawn based on
    Equation~\ref{eq:da_dt}), assuming $Q_\star' = 10^7$.  WASP-4b has
    a relatively short orbital decay timescale, although it is not as
    extreme a case in this regard as it is for eccentricity damping.
    {\bf \it Bottom:}
    A Hertzsprung-Russell diagram for hot Jupiter hosts. WASP-4
    appears to be on the main sequence.
    \label{fig:context}
  }
\end{figure}

@@

\subsection{Applegate effect}
Some eclipsing binaries exhibit period modulations with amplitudes of
$\lesssim 0.05\,{\rm days}$ over timescales of decades \citep[{\it
    e.g.},][]{soderhjelm_geometry_1980,hall_relation_1989}.
\citet{applegate_mechanism_1992} proposed a mechanism to explain these
modulations in which the internal structure of a magnetically active
star changes shape via cyclic exchange of angular momentum between the
inner and outer zones of the star.  This model could also apply to a
hot Jupiter orbiting a star with a convective zone.  The changing
gravitational quadrupole of the star would cause the orbit of the
planet to precess on the timescale of the stellar activity cycle.  An
essential difference between this process and apsidal precession is
that Applegate timing variations need not be strictly periodic
\citep[{\it e.g.},][Figure~12]{soderhjelm_geometry_1980}. This
mechanism would also produce transit and occultation timing deviations
of the same sign, while for apsidal precession they would have
opposite signs.  For WASP-4, \citet{watson_orbital_2010} estimated
that the Applegate effect could produce timing deviations of up to 15
seconds, depending on the modulation period of the stellar dynamo, and
the corresponding level of differential surface shear.  If this
analysis is accurate, then the Applegate mechanism cannot explain the
majority our observed $82$ second variation.

@@

\section{Call for additional observations}
\label{sec:future}

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.49\textwidth]{f6.pdf}
	\end{center}
  \vspace{-0.5cm}
	\caption{
    {\bf Further observations will be needed to confirm and understand
    the timing variations of WASP-4b.}
    Dots are as in Figure~\ref{fig:times}.  Lines are 100 random draws
    from the posteriors of the apsidal precession model (orange), and
    the orbital decay model (blue).    
		\label{fig:future}
	}
\end{figure}

@@

\clearpage
\newpage
\input{WASP-4b_transit_time_table.tex}

@@

\section{Verifying the TESS Time Stamps}
\label{sec:verify_tess}

@@

\begin{figure*}[ht!]
  \begin{center}
    \leavevmode
    \includegraphics[width=0.9\textwidth]{f7.pdf}
  \end{center}
  \vspace{-0.5cm}
  \caption{
    {\bf There is no evidence for a systematic offset between TESS
    times and the barycentric reference.} While the WASP-4b transits
    fell about 82 seconds earlier than expected, other well-observed
    hot Jupiters, in particular WASP-6b and WASP-18b, arrived on time.
    Ticks are observed TESS transit midtimes; the blue distribution is
    a kernel density estimate; the orange distribution is a gaussian
    centered on zero with standard deviation ($\sigma_{\rm
    predicted}$) calculated from the pre-TESS transit times.
    \label{fig:hjs}
  }
\end{figure*}
% JNW: I think the KDE needs to be removed and perhaps replaced with something
% else.  It gives the impression that the WASP-4 anomaly is only at
% the 2-sigma level, which is false.  The KDE illustrates the spread
% in values, but what is relevant is the standard deviation of the
% mean of the measurements, which is narrower than the KDE implies.
% I suggest replacing it with a Gaussian with a mean equal to the mean of the
% deviations, and a width equal to the uncertainty in the mean, i.e., the
% standard deviation divided by sqrt(N-1).

@@

We repeated all the data reduction and analysis steps described in
this paper for other hot Jupiters observed by TESS for which timing
data exists spanning many years.  First, we checked which hot Jupiters
were observed over the first two TESS sectors using a combination of
\texttt{tessmaps}\footnote{\url{github.com/lgbouma/tessmaps}} and
TEPCat \citep{southworth_homogeneous_2011}.  We then selected hot
Jupiters for which there were at least five distinct epochs reported
in the peer-reviewed literature.  We required that each observation be
of a single transit, that the midpoint be fit as a free parameter, and
that the time system be clearly documented.  Our final hot Jupiter
sample included WASP-4b, 5b, 6b, 18b, and 46b.  The collected and
measured times are given in Tables~5, 6, 7, and 8 for each.

@@

For each planet, we asked: what fraction of the posterior for $t_{\rm
offset}$ is consistent with an offset worse than $81.5$ seconds?  For
WASP-4b, the answer is unsurprisingly 50\%.  For WASP-6b, the most
constraining object, about 1 sample in 2 million is consistent with
such a timing offset ($4.9\sigma$).  For WASP-18b, 1 in 80 samples
would be consistent with this timing offset ($2.2\sigma$), and in
WASP-46b, the limit is 1 in 44 samples ($2.0\sigma$).  For WASP-5b,
the predicted time is too imprecise to rule out timing offsets at the
necessary amplitude.  Multiplying the three independent probabilities
for WASP-5b, 6b, and 18b, we can rule out $t_{\rm offset} < -81.5\
{\rm seconds}$ at $6.3\sigma$, or about about 1 part in 8 billion.

>>>>

\documentclass[12pt,twocolumn,tighten]{aastex62}
%\pdfoutput=1 %for arXiv submission
\usepackage{amsmath,amstext,amssymb}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}
\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{comment}

@@

\begin{abstract}
    The Transiting Exoplanet Survey Satellite (TESS) recently observed
    18 transits of the hot Jupiter WASP-4b.  The sequence of transits
    occurred $81.5 \pm 11.7$~seconds earlier than had been predicted,
    based on earlier data stretching back to 2007.  This is unlikely
    to be the result of a clock error, because TESS observations of
    other hot Jupiters (WASP-6b, 18b, and 46b) are compatible with a
    constant period, ruling out an 81.5-second offset at the
    6.4$\sigma$ level.  The 1.3-day orbital period of WASP-4b appears
    to be decreasing at a rate of $\dot{P} = -12.6 \pm 1.2$
    milliseconds per year.  This might be caused by tidal orbital
    decay or apsidal precession, although both interpretations have
    shortcomings.  The gravitational influence of a third body is another
    possibility, although at present there is scant evidence for such a
    body. Further observations are needed to confirm and
    understand the timing variation.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{New transits and system parameters}
\label{sec:observations}

\begin{figure}[t]
    \begin{center}
        \includegraphics[width=0.49\textwidth]{f1.png}
    \end{center}
    \vspace{-0.5cm}
    \caption{
      {\bf TESS observations of WASP-4b.} On the left, black points
      are TESS flux measurements, with a vertical offset applied. Blue
      curves are best-fit models. The numbers printed next to each
      lightcurve are the approximate transit times expressed in
      BJD minus 2{,}457{,}000.  The right side shows the
      residuals.
       \label{fig:lightcurves}
    }
\end{figure}

\begin{figure}[t]
    \begin{center}
        \includegraphics[width=0.49\textwidth]{f2.png}
    \end{center}
    \vspace{-0.5cm}
    \caption{
        {\bf Phase-folded lightcurve of WASP-4b.} Black points are
        TESS data. Yellow points are binned measurements.  The bottom
        panel shows the residuals.  The fit to the phase-folded
        transit (blue line) is used when measuring mid-transit times for
        the individual transits (Figure~\ref{fig:lightcurves}).
        \label{fig:phasefold}
    }
\end{figure}

@@

Using the cleaned PDC lightcurve, we used the Box Least Squares
algorithm \citep{kovacs_box-fitting_2002} to estimate the orbital
period, transit duration, and a reference epoch using the TESS data
alone.  Based on the results, we isolated the data within 4 transit
durations of each transit midpoint.  We then fitted all of the transit
data using the analytic formulae given by \citet{mandel_analytic_2002}
and implemented by \citet{kreidberg_batman_2015}.  We assumed the
orbit to be circular. The free parameters were the reference epoch,
the planet to star radius ratio $R_{\rm p}/R_\star$, the orbital
distance to stellar radius ratio $a/R_\star$, the inclination $i$, two
quadratic limb-darkening coefficients $(u_{\rm linear}, u_{\rm
  quad})$, and the orbital period $P$.

@@

To verify that the measured uncertainties are plausible, we computed
the reduced $\chi^2$ for a linear ephemeris fit to the measured TESS
transit times.  We found that $\chi^2 = 9.2$, with $n=16$ degrees of
freedom.  The variance of the $\chi^2$ distribution is $2n$, so we
would expect $\chi^2 16 \pm 5.7$.  Visually inspecting the residuals
showed that the error variance had been overestimated, so we
multiplied the measured TESS errors by a factor $f=0.76$, forcing a
reduced $\chi^2$ of unity.  This lowered the mean uncertainty of the
transit midtimes from $29.8$ to $22.6$ seconds.  We verified that
omitting this step did not appreciably alter any of our conclusions.

Figure~\ref{fig:lightcurves} shows the lightcurve of each transit, the
best-fit models, and the residuals.  Table~2 reports the mid-transit
times and their uncertainties.  After binning the residuals to 1-hour
windows, the lightcurves have an rms scatter of 586\,{\rm ppm}.  The
pre-launch TESS noise model\footnote{\url{github.com/lgbouma/tnm}} \citep{winn_photonflux_2013,Sullivan_2015}
would have predicted an error
budget consisting of the following terms added in quadrature:
410\,{\rm ppm} from photon-counting noise, 202\,{\rm ppm} from
detector read noise, and 673\,{\rm ppm} from the zodiacal background
light.  The level of background light appears to have been
overestimated.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Timing analysis}
\label{sec:timing}

\begin{figure}[t]
    \begin{center}
        \leavevmode
        \includegraphics[width=0.49\textwidth]{f3.pdf}
    \end{center}
    \vspace{-0.6cm}
    \caption{ {\bf TESS saw WASP-4b transit earlier than expected.}
      Both plots show the deviations between the observed and
      calculated transit times, where the calculation is based only on
      the pre-TESS data and assumes a constant period.  The blue bands
      depict the $\pm$$1\sigma$ credible interval of the predicted
      times.  {\it Top:} The full timing dataset spans 10 years. The
      darkest points correspond to the most precise data.  {\it
        Bottom:} Close-up of the TESS observations. The red band shows
      the average deviation of the TESS data, which is $81.5 \pm
      11.7\ {\rm seconds}$.
        \label{fig:arrived_early}
    }
\end{figure}

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{ {\bf Timing residuals and best-fit models for WASP-4b.}
		The residuals are the observed times minus the calculated times
		assuming a constant period.  The darkest points correspond to
		the most precise data. The constant-period model (gray line) is
		a poor description of the data.  Models with a uniformly
		decreasing period (blue) or apsidal precession (orange) provide
		better fits to the data.  The red square represents the
		combination of all the TESS data and is for display purposes
		only.  The models were fitted to all of the individual transit
		times.
		\label{fig:times}
	}
\end{figure*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Interpretation}
\label{sec:implications}

\begin{figure}[t]
  \begin{center}
    \includegraphics[width=0.38\textwidth]{f5.pdf}
  \end{center}
  \vspace{-0.5cm}
  \caption{
    {\bf WASP-4b in the context of other hot Jupiters.}
    Most of the data in these plots are from \citet{bonomo_gaps_2017},
    who measured the eccentricities using radial velocities.  The
    colored symbols highlight WASP-4, WASP-12 (which also shows
    evidence for a decreasing period), and the collection of hot
    Jupiters analyzed in Appendix A.
    {\bf \it Top:}
    The key parameters relevant to eccentricity damping.  Solid
    squares represent planets with a securely detected nonzero
    eccentricity. Lines of constant damping timescale are drawn based
    on Equation~\ref{eq:de_dt} and assuming $Q_{\rm p}' = 10^5$.
    WASP-4b has one of the shortest eccentricity damping timescales.
    {\bf \it Middle:} 
    Plotted are the key parameters relevant to orbital decay.  Lines
    of constant decay timescale are drawn based on
    Equation~\ref{eq:da_dt}), assuming $Q_\star' = 10^7$.  WASP-4b has
    a relatively short orbital decay timescale, although it is not as
    extreme a case in this regard as it is for eccentricity damping.
    {\bf \it Bottom:}
    A Hertzsprung-Russell diagram for hot Jupiter hosts. WASP-4
    appears to be on the main sequence.
    \label{fig:context}
  }
\end{figure}

@@

\subsection{Applegate effect}

Some eclipsing binaries exhibit period modulations with amplitudes of
$\lesssim 0.05\,{\rm days}$ over timescales of decades \citep[{\it
    e.g.},][]{soderhjelm_geometry_1980,hall_relation_1989}.
\citet{applegate_mechanism_1992} proposed a mechanism to explain these
modulations in which the internal structure of a magnetically active
star changes shape via cyclic exchange of angular momentum between the
inner and outer zones of the star.  This model could also apply to a
hot Jupiter orbiting a star with a convective zone.  The changing
gravitational quadrupole of the star would cause the orbit of the
planet to precess on the timescale of the stellar activity cycle.  An
essential difference between this process and apsidal precession is
that Applegate timing variations need not be strictly periodic
\citep[{\it e.g.},][Figure~12]{soderhjelm_geometry_1980}. This
mechanism would also produce transit and occultation timing deviations
of the same sign, while for apsidal precession they would have
opposite signs.  For WASP-4, \citet{watson_orbital_2010} estimated
that the Applegate effect could produce timing deviations of up to 15
seconds, depending on the modulation period of the stellar dynamo, and
the corresponding level of differential surface shear.  If this
analysis is accurate, then the Applegate mechanism cannot explain the
majority our observed $82$ second variation.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Call for additional observations}
\label{sec:future}

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.49\textwidth]{f6.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf Further observations will be needed to confirm and understand
    the timing variations of WASP-4b.} Dots are as in
    Figure~\ref{fig:times}.  Lines are 100 random draws from the
    posteriors of the apsidal precession model (orange), and the
    orbital decay model (blue).    
		\label{fig:future}
	}
\end{figure}

@@

%\clearpage
%\newpage
\input{WASP-4b_transit_time_table.tex}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Verifying the TESS Time Stamps}
\label{sec:verify_tess}

@@

\begin{figure*}[ht!]
  \begin{center}
    \leavevmode
    \includegraphics[width=0.9\textwidth]{f7.pdf}
  \end{center}
  \vspace{-0.5cm}
  \caption{
    {\bf There is no evidence for a systematic offset between TESS
    times and the barycentric reference.} While the WASP-4b transits
    fell about 82 seconds earlier than expected, other well-observed
    hot Jupiters, in particular WASP-6b and WASP-18b, arrived on time.
    Ticks are observed TESS transit midtimes; the orange distribution
    is a gaussian centered on zero with standard deviation
    ($\sigma_{\rm predicted}$) calculated from the pre-TESS transit
    times.  The blue distribution is a gaussian centered on the
    weighted average of the TESS times, with width equal to the
    uncertainty in the mean, {\it i.e.}, the standard deviation
    of the TESS residual times divided by $\sqrt{N-1}$, with $N$ the
    number of transits.
    \label{fig:hjs}
  }
\end{figure*}

@@

We repeated all the data reduction and analysis steps described in
this paper for other hot Jupiters observed by TESS for which timing
data exists spanning many years.  First, we checked which hot Jupiters
were observed over the first three TESS sectors using a combination of
\texttt{tessmaps}\footnote{\url{github.com/lgbouma/tessmaps}} and
TEPCat \citep{southworth_homogeneous_2011}.  We then selected hot
Jupiters for which there were at least five distinct epochs reported
in the peer-reviewed literature.  We required that each observation be
of a single transit, that the midpoint be fit as a free parameter, and
that the time system be clearly documented.  Our final hot Jupiter
sample included WASP-4b, 5b, 6b, 18b, and 46b.  The collected and
measured times are given in Tables~5, 6, 7, and 8 for each.

@@

For each planet, we asked: what fraction of the posterior for $t_{\rm
offset}$ is consistent with an offset worse than $81.5$ seconds?  For
WASP-4b, the answer is unsurprisingly 50\%.  For WASP-6b, the most
constraining object, about 1 sample in 2 million is consistent with
such a timing offset ($4.9\sigma$).  For WASP-18b, 1 in 103 samples
would be consistent with this timing offset ($2.3\sigma$), and in
WASP-46b, the limit is 1 in 49 samples ($2.0\sigma$).  For WASP-5b,
the predicted time is too imprecise to rule out timing offsets at the
necessary amplitude.  Multiplying the three independent probabilities
for WASP-5b, 6b, and 18b, we can rule out $t_{\rm offset} < -81.5\
{\rm seconds}$ at $6.4\sigma$, or about about 1 part in 11 billion.
